What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-16 lda-paper.tex

\section{Real Introduction}

@@

@@

Topic analysis often allows for a single document, such as a commit
message, to be related to multiple documents. This maps well to
commits which often have more than one purpose.

Commits in source control systems (SCSs) can have multiple
purposes. Thus we hope that our research will help uncover these
multiple purposes that manifest themselves as topics interleaved
within the commits.  Others have demonstrated that topic analysis
techniques, such as Latent Semantic Indexing (LSI) and Latent
Dirichlet Allocation (LDA), can aid in separating topics from these
mixed comments. These topics often describe distinct ideas that are
interleaved throughout the development. A topic represents both a word
distribution and a group of commit log comments that are related to
each other by their content.  In this case a topic is a set of tokens.

\shrinkit
\section{Introduction}
\shrinkit

%?
What happened in the previous maintenance or development iteration?
What were the developers working on? What was the developer in the
next cubicle working on?  Which common topics and issues were dealt
with in the current release of the software? What were the topics of
the previous release?  Given the requirements agreed to at the start
of the iteration did our developers work on them? What else did they
work on?

Imagine that a development team had agreed upon a set of features to
implement for a development iteration, but these features were not
finished by the end of the iteration. The developers insist they
focussed on those features, yet their manager is not sure what
happened. In a scenario like this, topic analysis can help tease out
the topics of development that the developers were focussed on. Topic
analysis could highlight the orthogonal issues that developers were
spending time on.  Topic analysis extracts groups of words from
documents (commit log comments) that are word distributions, topics,
which characterize clusters of documents. These extracted topics often
correlate with actual development topics that the developers
discussed. By applying topic analysis locally to an iteration, both
the developers and managers might be able to see what were the topics
of development during that iteration. %XXX RM during that iteration

%XXX RM 
Commits in source control systems (SCSs) can have multiple
purposes. Thus we hope that our research will help uncover these
multiple purposes that manifest themselves as topics interleaved
within the commits.  Others have demonstrated that topic analysis
techniques, such as Latent Semantic Indexing (LSI) and Latent
Dirichlet Allocation (LDA), can aid in separating topics from these
mixed comments. These topics often describe distinct ideas that are
interleaved throughout the development. A topic represents both a word
distribution and a group of commit log comments that are related to
each other by their content.  In this case a topic is a set of tokens.

% We suppose this could help us to segment the revisions on the time
% line to discover parts of an iteration.

Topic analysis can aid in partitioning a project's
time-line into periods of developer focus. By breaking apart an
iteration into sets of topics and trends (topics that recur), we may
be able to recognize the underlying software development process from
these commits. Alternatively, we can determine what particular
maintenance task was being performed at a given time.

We propose to extend existing topic analysis techniques by applying
them to windows of documents over time. We hope that by
looking %XX X ADDED
at topic clusters during periods or windows over time we can identify
ongoing areas of focus on a select group of topics as well reflect
more intermittent topics. Figure \ref{fig:lda} illustrates the kind of
visualization we want to automatically generate. We want to see topics
that are unique to a certain time period, displayed across the time
axis. Those topics that recur, or occur over a larger period are
plotted continuously. In our example we have titled each topic with a
single word drawn from itself.

In this paper we explore how topics shift over time in the SCS of a
project, using several open source database systems as examples. We
analyze commit log comments in each time window and we extract the
topics of that time window. We expect that topics will change over
time and the similarities and differences in these topics will
indicate developer focus and changes in developer focus as it changes
over time.

Our contributions include:
\begin{itemize}
\item Demonstrating the value of windowed topic analysis using trends.
\item Multiple visualizations of topics and trends over time.
\item An exploratory case study using these techniques on several open source database systems.
\end{itemize}

\shrinkit
\section{Background}
\shrinkit

>>>>

\section{Introduction}

@@

Topic analysis often allows for a single document, such as a commit
message, to be related to multiple topics. This maps well to
commits which often have more than one purpose.  A topic represents
both a word distribution and a group of commit log comments that are
related to each other by their content.  In this case a topic is a set
of tokens.

@@

Figure \ref{fig:lda} illustrates the kind of visualization we want to
automatically generate. We want to see topics that are unique to a
certain time period, displayed across the time axis. Those topics that
recur, or occur over a larger period are plotted continuously. In our
example we have titled each topic with a single word drawn from
itself.

In this paper we explore how topics shift over time in the source
control system (SCS) of a project, using several open source database
systems as examples. We analyze commit log comments in each time
window and we extract the topics of that time window. We expect that
topics will change over time and the similarities and differences in
these topics will indicate developer focus and changes in developer
focus as it changes over time.

Our contributions include:
\begin{itemize}
\item Demonstrating that most topics are local in scope, thus would be
  missed by a global topic analysis.
\item Multiple visualizations of topics and trends over time to aid
  communication and analysis of topics and trends.
\item An exploratory case study using these techniques on several open source database systems.
\end{itemize}

%%%   
%%%   
%%%   \shrinkit
%%%   \section{Introduction}
%%%   \shrinkit
%%%   
%%%   %?
%%%   What happened in the previous maintenance or development iteration?
%%%   What were the developers working on? What was the developer in the
%%%   next cubicle working on?  Which common topics and issues were dealt
%%%   with in the current release of the software? What were the topics of
%%%   the previous release?  Given the requirements agreed to at the start
%%%   of the iteration did our developers work on them? What else did they
%%%   work on?
%%%   
%%%   
%%%   Imagine that a development team had agreed upon a set of features to
%%%   implement for a development iteration, but these features were not
%%%   finished by the end of the iteration. The developers insist they
%%%   focussed on those features, yet their manager is not sure what
%%%   happened. In a scenario like this, topic analysis can help tease out
%%%   the topics of development that the developers were focussed on. Topic
%%%   analysis could highlight the orthogonal issues that developers were
%%%   spending time on.  Topic analysis extracts groups of words from
%%%   documents (commit log comments) that are word distributions, topics,
%%%   which characterize clusters of documents. These extracted topics often
%%%   correlate with actual development topics that the developers
%%%   discussed. By applying topic analysis locally to an iteration, both
%%%   the developers and managers might be able to see what were the topics
%%%   of development during that iteration. %XXX RM during that iteration
%%%   
%%%   
%%%   %XXX RM 
%%%   Commits in source control systems (SCSs) can have multiple
%%%   purposes. Thus we hope that our research will help uncover these
%%%   multiple purposes that manifest themselves as topics interleaved
%%%   within the commits.  Others have demonstrated that topic analysis
%%%   techniques, such as Latent Semantic Indexing (LSI) and Latent
%%%   Dirichlet Allocation (LDA), can aid in separating topics from these
%%%   mixed comments. These topics often describe distinct ideas that are
%%%   interleaved throughout the development. A topic represents both a word
%%%   distribution and a group of commit log comments that are related to
%%%   each other by their content.  In this case a topic is a set of tokens.
%%%   
%%%   
%%%   % We suppose this could help us to segment the revisions on the time
%%%   % line to discover parts of an iteration.
%%%   
%%%   Topic analysis can aid in partitioning a project's
%%%   time-line into periods of developer focus. By breaking apart an
%%%   iteration into sets of topics and trends (topics that recur), we may
%%%   be able to recognize the underlying software development process from
%%%   these commits. Alternatively, we can determine what particular
%%%   maintenance task was being performed at a given time.
%%%   
%%%   We propose to extend existing topic analysis techniques by applying
%%%   them to windows of documents over time. We hope that by
%%%   looking %XX X ADDED
%%%   at topic clusters during periods or windows over time we can identify
%%%   ongoing areas of focus on a select group of topics as well reflect
%%%   more intermittent topics. Figure \ref{fig:lda} illustrates the kind of
%%%   visualization we want to automatically generate. We want to see topics
%%%   that are unique to a certain time period, displayed across the time
%%%   axis. Those topics that recur, or occur over a larger period are
%%%   plotted continuously. In our example we have titled each topic with a
%%%   single word drawn from itself.
%%%   
%%%   In this paper we explore how topics shift over time in the SCS of a
%%%   project, using several open source database systems as examples. We
%%%   analyze commit log comments in each time window and we extract the
%%%   topics of that time window. We expect that topics will change over
%%%   time and the similarities and differences in these topics will
%%%   indicate developer focus and changes in developer focus as it changes
%%%   over time.
%%%   
%%%   Our contributions include:
%%%   \begin{itemize}
%%%   \item Demonstrating the value of windowed topic analysis using trends.
%%%   \item Multiple visualizations of topics and trends over time.
%%%   \item An exploratory case study using these techniques on several open source database systems.
%%%   \end{itemize}
%%%   
\shrinkit
\section{Background}
\shrinkit
